Put Your Money Where Your Mouth Is: Prediction Markets and Climate Change

### 2016-03-07 paper.Rmd
Plotting code for paper.

We present a simulation of a climate prediction market. Traders adapt their beliefs about the future global temperatures based on the monetary performance of their neighboring traders in a social network. We conduct experiments with the model to determine how a variety of market factors and the climate data-generating process affect whether climate prediction markets foster a convergence of market participants' beliefs regarding a true model of the global climate.

@@

As a validation that the market is operating correctly, we run the market with actual temperatures 1880 to 2015 and market betting from 1931 to 2014. As warming signal begins to show up in 1980s, traders begin to converge toward log(CO2) model.

Jonathan plot here.

@@

```{r sa, eval=TRUE, echo=FALSE, message=FALSE, htmlcap=figRef("sa", "Estimated effects of model parameters on convergence of beliefs in future scenario."), fig.width=3.8, fig.height=4.5}
# library(eat)
# load("output/src_future.Rda")
# plot(src_future, outcome_var = "Convergence") + theme_classic() + theme(text=element_text(family='Palatino'))

@@

```{r time, eval=TRUE, echo=FALSE, message=FALSE, htmlcap=figRef("time", "Time"), fig.width=5, fig.height=9}
source("utils/time_plot.R")
time_plot() + theme(text=element_text(family='Palatino'))
```

@@

>>>>

We present a simulation of a climate prediction market. Traders adapt their beliefs about future global temperatures based on the monetary performance of their neighboring traders in a social network. We conduct experiments with the model to determine how a variety of market factors and the climate data-generating process affect whether climate prediction markets foster a convergence of market participants' beliefs regarding a true model of the global climate.

@@

As a validation that the market is operating correctly, we run the market with actual temperatures 1880 to 2015 and market betting from 1931 to 2014. As warming signal begins to show up in 1980s, traders begin to converge toward log(CO2) model `r figRef("time")`.

@@

```{r sa, eval=TRUE, echo=FALSE, message=FALSE, htmlcap=figRef("sa", "Estimated effects of model parameters on convergence of beliefs in future scenario."), fig.width=3, fig.height=3.5}
# library(eat)
# load("output/src_future.Rda")
# plot(src_future, outcome_var = "Convergence") + theme_classic() + theme(text=element_text(family='Palatino'))

@@

```{r time, eval=TRUE, echo=FALSE, message=FALSE, htmlcap=figRef("time", "Convergence over trading sequences."), fig.width=10.5, fig.height=8.5}
source("utils/time_plot.R")
p1 <- history_box() + theme(text=element_text(family='Palatino'))
p2 <- future_box() + theme(text=element_text(family='Palatino'))
multi_plot(p1, p2, cols=2)
```

@@

Our code for the model is available at [johnjnay.com/predictMarket](http://johnjnay.com/predictMarket).
